Uncovering Distributed System Bugs\\ during Testing (not Production!)

### 2015-08-21 casestudies.tex
new figure
Migration case study: add references to figures from text.

% N.B. Artifact Services is mentioned at http://research.microsoft.com/en-us/people/schulte/.  Hopefully it's OK to reveal that it was the system in this case study. ~ Matt 2015-08-17
The initial motivation for MigratingTable was to solve a scaling problem for Artifact Services, an internal Microsoft system with a data set that is sharded across tables in different Azure storage accounts because it exceeds the limit on traffic supported by a single Azure storage account.  As the traffic continues to grow over time, we will need to reshard the data set across a greater number of Azure storage accounts without interrupting service.  During such a resharding, our sharding manager will identify each key range that should migrate to a different table, and we will use a separate MigratingTable instance for each such key range to actually perform the migration.  MigratingTable may also be useful to migrate data to a table with different values of configuration parameters that Azure does not support changing on an existing table, such as geographic location.

@@

% N.B. SpecTable = InMemoryTableWithHistory in the current codebase. ~ Matt 2015-08-17
Since the specification is deterministic under sequential calls except for the results of multi-page reads, we decided the easiest way to formulate it for automated testing was to write an in-memory reference implementation called SpecTable.  Given a multi-page read, SpecTable can actually produce a list of all valid results.  Our correctness property is then:
\begin{quote}
For every execution trace of a collection of MigratingTables backed by the same pair of SpecTables (which nondeterministically choose one of the valid results for each multi-page read), there exists a linearization of the combined input history such that the output in the original trace matches the output of a ``reference'' SpecTable on the linearized input.
\end{quote}
%
\def\term#1{\emph{#1}}
We instrumented MigratingTable to report the \term{linearization point} of each input call, which in our case is always one of the corresponding \term{backend calls} to the backend tables (often the last).  Specifically, after each backend call completes, MigratingTable reports whether it was the linearization point, which may depend on the result of the call.  This makes it possible to verify the correctness property as the system executes.  We have a \psharp \term{tables machine} containing all three SpecTables and a collection of \term{service machines} each containing a MigratingTable.  Each service machine issues a random sequence of input calls to its MigratingTable, which sends backend calls to the tables machine.  When MigratingTable reports the linearization point of an input call, the service machine sends that input call to the reference table.  When an input call completes, the service machine checks that the results from the MigratingTable and the reference table agree.  \psharp controls the interleaving of the backend calls.  To ensure that the reference table is never observed to be out of sync with the backend tables, after the tables machine processes a backend call, it enters a state that defers further backend calls until MigratingTable has reported whether the backend call was a linearization point and (if so) the call to the reference table has been made.  We use the \psharp nondeterminism API to generate the input calls, so in principle an exhaustive \psharp behavior exploration strategy such as DFS could be used to exhaustively test MigratingTable up to some bound.

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{img/mocked_migration}
\caption{Draft.}
\label{fig:mockedmigration}
\end{figure}

% N.B. Artifact Services is mentioned at http://research.microsoft.com/en-us/people/schulte/.  Hopefully it's OK to reveal that it was the system in this case study. ~ Matt 2015-08-17
The initial motivation for MigratingTable was to solve a scaling problem for Artifact Services, an internal Microsoft system with a data set that is sharded across tables in different Azure storage accounts because it exceeds the limit on traffic supported by a single Azure storage account.  As the traffic continues to grow over time, we will need to reshard the data set across a greater number of Azure storage accounts without interrupting service.  During such a resharding, our sharding manager will identify each key range that should migrate to a different table, and we will use a separate MigratingTable instance for each such key range to actually perform the migration (Figure~\ref{fig:livemigration}).  MigratingTable may also be useful to migrate data to a table with different values of configuration parameters that Azure does not support changing on an existing table, such as geographic location.

@@

% N.B. SpecTable = InMemoryTableWithHistory in the current codebase. ~ Matt 2015-08-17
Since the specification is deterministic under sequential calls except for the results of multi-page reads, we decided the easiest way to formulate it for automated testing was to write an in-memory reference implementation called SpecTable.  Given a multi-page read, SpecTable can actually produce a list of all valid results.  Our correctness property is then:
\begin{quote}
For every execution trace of a collection of MigratingTables backed by the same pair of SpecTables (which nondeterministically choose one of the valid results for each multi-page read), there exists a linearization of the combined input history such that the output in the original trace matches the output of a ``reference'' SpecTable on the linearized input.
\end{quote}
%
\def\term#1{\emph{#1}}
We instrumented MigratingTable to report the \term{linearization point} of each input call, which in our case is always one of the corresponding \term{backend calls} to the backend tables (often the last).  Specifically, after each backend call completes, MigratingTable reports whether it was the linearization point, which may depend on the result of the call.  This makes it possible to verify the correctness property as the system executes.  We have a \psharp \term{tables machine} containing all three SpecTables and a collection of \term{service machines} each containing a MigratingTable (Figure~\ref{fig:mockedmigration}).  Each service machine issues a random sequence of input calls to its MigratingTable, which sends backend calls to the tables machine.  When MigratingTable reports the linearization point of an input call, the service machine sends that input call to the reference table.  When an input call completes, the service machine checks that the results from the MigratingTable and the reference table agree.  \psharp controls the interleaving of the backend calls.  To ensure that the reference table is never observed to be out of sync with the backend tables, after the tables machine processes a backend call, it enters a state that defers further backend calls until MigratingTable has reported whether the backend call was a linearization point and (if so) the call to the reference table has been made.  We use the \psharp nondeterminism API to generate the input calls, so in principle an exhaustive \psharp behavior exploration strategy such as DFS could be used to exhaustively test MigratingTable up to some bound.
